Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-08-06 scagnostics.Rmd
Moved application guidelines.

- Scaling and standardization of the data
- Index function selection and if necessary formatting according to the guided tour requirements, i.e. a function taking matrix input and returning the index value
- Calling the guided tour, for exploration this can be done via the `tourr::animate` function, for recording the results `tourr::save_history` should be used, examples are given in the documentation of the `tourr::guided_tour` function
- Things to explore: different indexes, different starting planes, different optimisation options, different ways of reducing dimensionality prior to the guided tour run

This section describes the application of these projection pursuit indices to find two-dimensional structure in two multidimensional gravitational waves problems.
\textcolor{red}{These illustrate different ways of exploring real data using projection pursuit, showcasing the dependence of the results on index function, starting plane and variable selection.}

@@

>>>>

This section describes the application of these projection pursuit indices to find two-dimensional structure in two multidimensional gravitational waves problems.

@@

## Application guide

1. Scaling and standardization of the data
2. Index function selection and if necessary formatting according to the guided tour requirements, i.e. a function taking matrix input and returning the index value
3. Calling the guided tour with the data and index function via:
    + for exploration this can be done via the `tourr::animate` function
    + for recording the results `tourr::save_history` should be used
4. Exploring how the results depend on choices made (index function, starting planes, optimisation method, reducing dimensionality)
